---
title: "DHS Myanmar"
author: Hnin & Wai
format: dashboard
server: shiny
---


```{r}
#| context: setup
# loading required packages

library(tidyverse)
library(rnaturalearth)
library(rnaturalearthdata)
library(sf)
library(haven)
library(survey)
library(patchwork)
library(modelsummary)
```


```{r}
# data importing

dhs_mm <- read_csv(here::here("data", "dhs_mm.csv"))

# Variable selection based on research question

dhs_select <- dhs_mm %>% 
  select(caseid, v005, v013, v021, v023, v024, v025, v106, v190, v301, v312, v313, v502, v626a)


# Creating new and modifying existing variables  

dhs_final <- dhs_select %>% 
  mutate(wt = v005/1000000,
         psu = v021,
         strat = v023) %>% # sampling weight
  filter(v502 == 1) %>% # current married women
  mutate(
    age = case_when(
      v013 == 1 ~ "15-19",
      v013 == 2 ~ "20-24",
      v013 == 3 ~ "25-29",
      v013 == 4 ~ "30-34",
      v013 == 5 ~ "35-39",
      v013 == 6 ~ "40-44",
      v013 == 7 ~ "45-49"
    ),
    location = case_when(
      v024 == 1 ~ "Kachin",
      v024 == 2 ~ "Kayah",
      v024 == 3 ~ "Kayin",
      v024 == 4 ~ "Chin",
      v024 == 5 ~ "Sagaing",
      v024 == 6 ~ "Tanintharyi",
      v024 == 7 ~ "Bago",
      v024 == 8 ~ "Magway",
      v024 == 9 ~ "Mandalay",
      v024 == 10 ~ "Mon",
      v024 == 11 ~ "Rakhine",
      v024 == 12 ~ "Yangon",
      v024 == 13 ~ "Shan",
      v024 == 14 ~ "Ayeyarwady",
      v024 == 15 ~ "Naypyitaw"
    ),
    residence = case_when(
      v025 == 1 ~ "urban",
      v025 == 2 ~ "rural"
    ),
    education = case_when(
      v106 == 0 ~ "no education",
      v106 == 1 ~ "primary",
      v106 == 2 ~ "secondary",
      v106 == 3 ~ "higher"
    ),
    wealth_index = case_when(
      v190 == 1 ~ "poorest",
      v190 == 2 ~ "poorer",
      v190 == 3 ~ "middle",
      v190 == 4 ~ "richer",
      v190 == 5 ~ "richest"
    ),
    method = case_when(
      v312 == 0 ~ "no_use",
      v312 == 1 ~ "pill",
      v312 == 2 ~ "IUD",
      v312 == 3 ~ "injection",
      v312 == 5 ~ "male_condom",
      v312 == 6 ~ "female_sterilization",
      v312 == 7 ~ "male_sterilization",
      v312 == 8 ~ "periodic_abstinence",
      v312 == 9 ~ "withdrawal",
      v312 == 10 ~ "other_traditional",
      v312 == 11 ~ "implant",
      v312 == 13 ~ "lac_amenorrhoea",
      v312 == 17 ~ "other_modern")
  ) %>% 
  mutate(
    knowledge = ifelse(v301 %in% c(3,2), 1, 0),
    practice = ifelse(v313 %in% c(3,2,1), 1,0),
    location_bi = ifelse(v024 %in% c(1, 2, 3, 4, 10, 11 & 13), 0, 1)
  ) %>% 
  mutate(
    location_bi = case_when(
      location_bi == 0 ~ "state",
      location_bi == 1 ~ "region"
    )
  ) %>% 
  mutate(knowledge = factor(knowledge),
         practice = factor(practice))
```


```{r}
# releveling variable categories

dhs_final$education <- relevel(factor(dhs_final$education), ref = "no education")

dhs_final$age <- relevel(factor(dhs_final$age), ref = "15-19")

dhs_final$location_bi <- relevel(factor(dhs_final$location_bi), ref = "state")

dhs_final$residence <- relevel(factor(dhs_final$residence), ref = "rural")

dhs_final$wealth_index <- relevel(factor(dhs_final$wealth_index), ref = "poorest")

```


```{r}
# sampling weight

mysurvey <- svydesign(ids = ~psu, strata = ~strat, weights =~wt, data = dhs_final)
```


```{r}
# Creating dataframe for mapping

world <- ne_countries(returnclass = "sf")
myanmar <- ne_states(country = "Myanmar", returnclass = "sf")
```

# Background

## Row {.tabset}

### World map

```{r}
world_mm_map <- world %>%
  mutate(myanmar = case_when(
    name_long == "Myanmar" ~ 1,
    TRUE ~ 0
  )) %>% 
  ggplot(aes(fill = factor(myanmar))) +
  geom_sf() +
  scale_fill_manual(values = c("0" = "gray", "1" = "red")) + 
  theme_minimal() +
  theme(legend.position = "none") +
  labs(title = "Home to longest civil war in the world from 1962 to present day")

world_mm_map
```

### Demographics & Ethnicity

Myanmar has a population of 52 million, comprising approximately 135 ethnic groups. The country is divided into 7 states and 7 regions. The dominant ethnic group is the "Bamar," accounting for 68% of the total population. The majority of the Bamar population resides in the regions (green areas), while more than 100 ethnic groups inhabit the states (red areas). All the red areas are affected by armed conflicts between the Bamar military and ethnic armed groups. The oppression by the Bamar military against ethnic minorities has resulted in significant disparities between the states and regions.

```{r}
# Administratively, 7 states and 7 regions

mm_map1 <- myanmar %>% 
  ggplot()+
  geom_sf(aes(fill = name, color = name)) +
  geom_sf_text(aes(label = name), size = 2.5) +
  theme_void() +
  theme(legend.position = "none")

```


```{r}
# Dividing into two groups

region_colors <- c(
  "Ayeyarwady" = "green",
  "Bago" = "green",
  "Chin" = "red",
  "Kachin" = "red",
  "Kayah" = "red",
  "Kayin" = "red",
  "Magway" = "green",
  "Mandalay" = "green",
  "Mon" = "red",
  "Rakhine" = "red",
  "Sagaing" = "green",
  "Shan" = "red",
  "Tanintharyi" = "green",
  "Yangon" = "green"
)

mm_map2 <- myanmar %>% 
  mutate(ethnicity = ifelse(name %in% c("Kachin", "Kayah", "Kayin", "Kachin", "Chin", "Mon", "Rakhine", "Shan"), "State", "Region")) %>% 
  ggplot() +
  geom_sf(data = myanmar, aes(fill = name)) + 
  scale_fill_manual(values = region_colors) + 
  geom_sf_text(aes(label = ethnicity), size = 2) +
  theme_void() +
  theme(legend.position = "none")
```



```{r}
mm_map1
```


```{r}
mm_map2
```

# Contraceptive Knowledge

## Row {.tabset}

### age

```{r}

know_a <- svyby(
  ~knowledge,
  by = ~age,
  design = mysurvey,
  FUN = svymean,
  vartype = c("se", "ci")
) %>% 
  mutate(age = factor(age, levels = c("15-19", "20-24", "25-29", "30-34", "35-39", "40-44", "45-49"))) %>% 
  ggplot(aes(age, knowledge1)) +
  geom_col(aes(fill = age)) + 
  scale_y_continuous(labels = scales::percent_format(scale = 100))+
  labs(x = "Age Group", y = "Contraceptive Knowledge", title = "Figure 1: Younger and older age groups have lesser knowledge of contraception") + 
  theme_minimal() +
  theme(legend.position = "none", plot.title = element_text(face = "bold"))

know_a

```

### education

```{r}
know_e <- svyby(
  ~knowledge,
  by = ~education,
  design = mysurvey,
  FUN = svymean,
  vartype = c("se", "ci")
) %>% 
  mutate(education = factor(education, levels = c("no education", "primary", "secondary", "higher"))) %>% 
  ggplot(aes(education, knowledge1)) +
  geom_col(aes(fill = education)) + 
  scale_y_continuous(labels = scales::percent_format(scale = 100))+
  labs(x = "Education level", y = "Contraceptive Knowledge", title = "Women with lower education level have lesser knowledge of contraception") + 
  theme_minimal() +
  theme(legend.position = "none", plot.title = element_text(face = "bold"))

know_e



```

### residence

```{r}

know_r <- svyby(
  ~knowledge,
  by = ~residence,
  design = mysurvey,
  FUN = svymean,
  vartype = c("se", "ci")
) %>% 
  ggplot(aes(residence, knowledge1)) +
  geom_col(aes(fill = residence)) + 
  scale_y_continuous(labels = scales::percent_format(scale = 100))+
  labs(x = "Residence", y = "Contraceptive Knowledge", title = "Women frm rural have slightly less knowledge") + 
  theme_minimal() +
  theme(legend.position = "none", plot.title = element_text(face = "bold"))

know_r


```


### location

```{r}
know_l <- svyby(
  ~knowledge,
  by = ~location_bi,
  design = mysurvey,
  FUN = svymean,
  vartype = c("se", "ci")
) %>% 
  ggplot(aes(location_bi, knowledge1)) +
  geom_col(aes(fill = location_bi)) + 
  scale_y_continuous(labels = scales::percent_format(scale = 100))+
  labs(x = "Location", y = "Contraceptive Practice", title = "Women from state have lower contraceptive use") + 
  theme_minimal() +
  theme(legend.position = "none")

know_l
```


### wealth index 

```{r}

know_w <- svyby(
  ~knowledge,
  by = ~wealth_index,
  design = mysurvey,
  FUN = svymean,
  vartype = c("se", "ci")
) %>% 
  mutate(wealth_index = factor(wealth_index, levels = c("poorest", "poorer", "middle", "richer", "richest"))) %>% 
   ggplot(aes(wealth_index, knowledge1)) +
  geom_col(aes(fill = wealth_index)) + 
  scale_y_continuous(labels = scales::percent_format(scale = 100))+
  labs(x = "Wealth Index", y = "Contraceptive Knowledge", title = "Relatively poorer women have lesser knowledge of contraception") + 
  theme_minimal() +
  theme(legend.position = "none", plot.title = element_text(face = "bold"))

know_w

```


# Contraceptive practice 

## Row {.tabset}

### age

```{r}
#| title: practice by age group


prac_a <- svyby(
  ~practice,
  by = ~age,
  design = mysurvey,
  FUN = svymean,
  vartype = c("se", "ci")
) %>% 
  mutate(age = factor(age, levels = c("15-19", "20-24", "25-29", "30-34", "35-39", "40-44", "45-49"))) %>% 
  ggplot(aes(age, practice1)) +
  geom_col(aes(fill = age)) + 
  scale_y_continuous(labels = scales::percent_format(scale = 100))+
  labs(x = "Age Group", y = "Contraceptive Practice", title = "Younger and older age groups have lower contraceptive use") + 
  theme_minimal() +
  theme(legend.position = "none")

prac_a
```

### education

```{r}
prac_e <- svyby(
  ~practice,
  by = ~education,
  design = mysurvey,
  FUN = svymean,
  vartype = c("se", "ci")
) %>% 
  mutate(education = factor(education, levels = c("no education", "primary", "secondary", "higher"))) %>% 
  ggplot(aes(education, practice1)) +
  geom_col(aes(fill = education)) + 
  scale_y_continuous(labels = scales::percent_format(scale = 100))+
  labs(x = "Education level", y = "Contraceptive Practice", title = "Women with lower level of education have significantly low use of contraception") + 
  theme_minimal() +
  theme(legend.position = "none")

prac_e
```

### residence

```{r}

prac_r <- svyby(
  ~practice,
  by = ~residence,
  design = mysurvey,
  FUN = svymean,
  vartype = c("se", "ci")
) %>% 
  ggplot(aes(residence, practice1)) +
  geom_col(aes(fill = residence)) + 
  scale_y_continuous(labels = scales::percent_format(scale = 100))+
  labs(x = "Residence", y = "Contraceptive Practice", title = "Wome from rural have lower contraceptive use") + 
  theme_minimal() +
  theme(legend.position = "none")
prac_r
```

### location

```{r}
prac_l <- svyby(
  ~practice,
  by = ~location_bi,
  design = mysurvey,
  FUN = svymean,
  vartype = c("se", "ci")
) %>% 
  ggplot(aes(location_bi, practice1)) +
  geom_col(aes(fill = location_bi)) + 
  scale_y_continuous(labels = scales::percent_format(scale = 100))+
  labs(x = "Location", y = "Contraceptive Practice", title = "Women from state have lower contraceptive use") + 
  theme_minimal() +
  theme(legend.position = "none")

prac_l
```

### wealth index 

```{r}

prac_w <- svyby(
  ~practice,
  by = ~wealth_index,
  design = mysurvey,
  FUN = svymean,
  vartype = c("se", "ci")
) %>% 
  mutate(wealth_index = factor(wealth_index, levels = c("poorest", "poorer", "middle", "richer", "richest"))) %>% 
   ggplot(aes(wealth_index, practice1)) +
  geom_col(aes(fill = wealth_index)) + 
  scale_y_continuous(labels = scales::percent_format(scale = 100))+
  labs(x = "Wealth Index", y = "Contraceptive Practice", title = "Relatively poorer women have lower contraceptive use") + 
  theme_minimal() +
  theme(legend.position = "none")

prac_w

```


# Unmet need

```{r}
# To filter only unmet and met need from total cohort which includes no unmet need, never had sex ... check details in data dictionary

dhs_unmet <- dhs_final %>% 
  filter(v626a %in% c(1,2,3,4)) %>% 
  mutate(unmet_need = ifelse(v626a %in% c(1,2), 1, 0)) %>% 
  mutate(unmet_need = factor(unmet_need))
```


```{r}
# another survey weight for unmet need because of dataset changes

mysurvey2 <- svydesign(ids = ~psu, strata = ~strat, weights =~wt, data = dhs_unmet)  
```


## Row {.tabset}

### age

```{r}
#| title: unmet need by age group

unmet_a <- svyby(
  ~unmet_need,
  by = ~age,
  design = mysurvey2,
  FUN = svymean,
  vartype = c("se", "ci")
) %>% 
  mutate(age = factor(age, levels = c("15-19", "20-24", "25-29", "30-34", "35-39", "40-44", "45-49"))) %>% 
  ggplot(aes(age, unmet_need1)) +
  geom_col(aes(fill = age)) + 
  scale_y_continuous(labels = scales::percent_format(scale = 100))+
  labs(x = "Age Group", y = "Unmet Need", title = "Younger and older age groups have higher contraceptive unmet need") + 
  theme_minimal() +
  theme(legend.position = "none")

unmet_a
```

### education

```{r}
unmet_e <- svyby(
  ~unmet_need,
  by = ~education,
  design = mysurvey2,
  FUN = svymean,
  vartype = c("se", "ci")
) %>% 
  mutate(education = factor(education, levels = c("no education", "primary", "secondary", "higher"))) %>% 
  ggplot(aes(education, unmet_need1)) +
  geom_col(aes(fill = education)) + 
  scale_y_continuous(labels = scales::percent_format(scale = 100))+
  labs(x = "Education", y = "Unmet Need", title = "Women with lower level of education have higher contraceptive unmet need") + 
  theme_minimal() +
  theme(legend.position = "none")

unmet_e
```

### residence

```{r}
#| title: unmet need by residence

unmet_r <- svyby(
  ~unmet_need,
  by = ~residence,
  design = mysurvey2,
  FUN = svymean,
  vartype = c("se", "ci")
) %>% 
  ggplot(aes(residence, unmet_need1)) +
  geom_col(aes(fill = residence)) + 
  scale_y_continuous(labels = scales::percent_format(scale = 100))+
  labs(x = "Residence", y = "Unmet Need", title = "Women from rural have higher contraceptive unmet need") + 
  theme_minimal() +
  theme(legend.position = "none")

unmet_r
```

### location

```{r}

unmet_l <- svyby(
  ~unmet_need,
  by = ~location_bi,
  design = mysurvey2,
  FUN = svymean,
  vartype = c("se", "ci")
) %>% 
  ggplot(aes(location_bi, unmet_need1)) +
  geom_col(aes(fill = location_bi)) + 
  scale_y_continuous(labels = scales::percent_format(scale = 100))+
  labs(x = "Location", y = "Unmet Need", title = "Women from state have higher contraceptive unmet need") + 
  theme_minimal() +
  theme(legend.position = "none")

unmet_l
```

### wealth index 

```{r}

unmet_w <- svyby(
  ~unmet_need,
  by = ~wealth_index,
  design = mysurvey2,
  FUN = svymean,
  vartype = c("se", "ci")
) %>% 
  mutate(wealth_index = factor(wealth_index, levels = c("poorest", "poorer", "middle", "richer", "richest"))) %>% 
  ggplot(aes(wealth_index, unmet_need1)) +
  geom_col(aes(fill = wealth_index)) + 
  scale_y_continuous(labels = scales::percent_format(scale = 100))+
  labs(x = "Wealth Index", y = "Unmet Need", title = "Relatively poorer women have higher contraceptive unmet need") + 
  theme_minimal() +
  theme(legend.position = "none")

unmet_w

```

# State Vs Region

## Row {.tabset}

```{r}
# Contraceptive knowledge by age and location

local_ka <- svyby(
  ~knowledge,
  by = ~ age + location_bi,
  design = mysurvey,
  FUN = svymean,
  vartype = c("se", "ci")
)


# Contraceptive knowledge by education and location

local_ke <- svyby(
  ~knowledge ,
  by = ~ education + location_bi,
  design = mysurvey,
  FUN = svymean,
  vartype = c("se", "ci")
)

# Contraceptive knowledge by residence and location
local_kr <- svyby(
  ~knowledge ,
  by = ~ residence + location_bi,
  design = mysurvey,
  FUN = svymean,
  vartype = c("se", "ci")
)

# Contraceptive knowledge by wealth index and location
local_kw <- svyby(
  ~knowledge ,
  by = ~ wealth_index + location_bi,
  design = mysurvey,
  FUN = svymean,
  vartype = c("se", "ci")
)


# knowledge by age and location

kal_plot <- local_ka %>%
  ggplot(aes(x = age, y = knowledge1, color = location_bi, group = location_bi)) +
  geom_point() +
  geom_smooth(se = FALSE) +
  facet_wrap(~location_bi) +
  scale_color_brewer(palette = "Set1")+
  scale_y_continuous(labels = scales::percent_format(scale = 100), 
                     limits = c(0.92, 1), 
                     breaks = seq(0.92, 1, by = 0.02)) +
  labs(x = "Age Group", y= "Knowledge")+
  theme_minimal()+
  theme(legend.position = "none", axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))


# knowledge by education and location

kel_plot <- local_ke %>%
  mutate(education = factor(education, levels = c("no education", "primary", "secondary", "higher"))) %>%
  ggplot(aes(x = education, y = knowledge1, color = location_bi, group = location_bi)) +
  geom_point() +
  geom_smooth(se = FALSE, method = lm) +
  facet_wrap(~location_bi) +
  scale_color_brewer(palette = "Set1")+
  scale_y_continuous(labels = scales::percent_format(scale = 100), 
                     limits = c(0.92, 1), 
                     breaks = seq(0.92, 1, by = 0.02)) +
  labs(x = "Education", y= NULL)+
  theme_minimal()+
  theme(legend.position = "none", axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
  

# knowledge by residence and location

krl_plot <- local_kr %>%
  ggplot(aes(x = residence, y = knowledge1, color = location_bi, group = location_bi)) +
  geom_point() +
  geom_smooth(se = FALSE, method = lm) +
  facet_wrap(~location_bi) +
  scale_color_brewer(palette = "Set1")+
  scale_y_continuous(labels = scales::percent_format(scale = 100), 
                     limits = c(0.92, 1), 
                     breaks = seq(0.92, 1, by = 0.02)) +
  labs(x = "Residence", y= "Knowledge")+
  theme_minimal()+
  theme(legend.position = "none", axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
  

# knowledge by wealth index and location

kwl_plot <- local_kw %>%
  mutate(wealth_index = factor(wealth_index, levels = c("poorest", "poorer", "middle", "richer", "richest"))) %>%
  ggplot(aes(x = wealth_index, y = knowledge1, color = location_bi, group = location_bi)) +
  geom_point() +
  geom_smooth(se = FALSE, method = lm) +
  facet_wrap(~location_bi) +
  scale_color_brewer(palette = "Set1")+
  scale_y_continuous(labels = scales::percent_format(scale = 100), 
                     limits = c(0.92, 1), 
                     breaks = seq(0.92, 1, by = 0.02)) +
  labs(x = "Wealth Index", y= NULL)+
  theme_minimal()+
  theme(legend.position = "none", axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))


# Contraceptive practice by age and location

local_pa <- svyby(
  ~practice ,
  by = ~ age + location_bi,
  design = mysurvey,
  FUN = svymean,
  vartype = c("se", "ci")
)


# Contraceptive practice by education and location

local_pe <- svyby(
  ~practice ,
  by = ~ education + location_bi,
  design = mysurvey,
  FUN = svymean,
  vartype = c("se", "ci")
)

# Contraceptive practice by residence and location
local_pr <- svyby(
  ~practice ,
  by = ~ residence + location_bi,
  design = mysurvey,
  FUN = svymean,
  vartype = c("se", "ci")
)

# Contraceptive practice by wealth index and location
local_pw <- svyby(
  ~practice ,
  by = ~ wealth_index + location_bi,
  design = mysurvey,
  FUN = svymean,
  vartype = c("se", "ci")
)


# Practice by age and location

pal_plot <- local_pa %>%
  ggplot(aes(x = age, y = practice1, color = location_bi, group = location_bi)) +
  geom_point() +
  geom_smooth(se = FALSE) +
  facet_wrap(~location_bi) +
  scale_color_brewer(palette = "Set1")+
  scale_y_continuous(labels = scales::percent_format(scale = 100), 
                     limits = c(0.25, 0.7), 
                     breaks = seq(0.25, 0.7, by = 0.1)) +
  labs(x = "Age Group", y= "Practice")+
  theme_minimal()+
  theme(legend.position = "none", axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

# practice by education and location

pel_plot <- local_pe %>%
  mutate(education = factor(education, levels = c("no education", "primary", "secondary", "higher"))) %>%
  ggplot(aes(x = education, y = practice1, color = location_bi, group = location_bi)) +
  geom_point() +
  geom_smooth(se = FALSE, method = lm) +
  facet_wrap(~location_bi) +
  scale_color_brewer(palette = "Set1")+
  scale_y_continuous(labels = scales::percent_format(scale = 100), 
                     limits = c(0.25, 0.7), 
                     breaks = seq(0.25, 0.7, by = 0.1)) +
  labs(x = "Education", y= NULL)+
  theme_minimal()+
  theme(legend.position = "none", axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

  

# practice by residence and location

prl_plot <- local_pr %>%
  ggplot(aes(x = residence, y = practice1, color = location_bi, group = location_bi)) +
  geom_point() +
  geom_smooth(se = FALSE, method = lm) +
  facet_wrap(~location_bi) +
  scale_color_brewer(palette = "Set1")+
  scale_y_continuous(labels = scales::percent_format(scale = 100), 
                     limits = c(0.25, 0.7), 
                     breaks = seq(0.25, 0.7, by = 0.1)) +
  labs(x = "Residence", y= "Practice")+
  theme_minimal()+
  theme(legend.position = "none", axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
  

# practice by wealth index and location

pwl_plot <- local_pw %>%
  mutate(wealth_index = factor(wealth_index, levels = c("poorest", "poorer", "middle", "richer", "richest"))) %>%
  ggplot(aes(x = wealth_index, y = practice1, color = location_bi, group = location_bi)) +
  geom_point() +
  geom_smooth(se = FALSE, method = lm) +
  facet_wrap(~location_bi) +
  scale_color_brewer(palette = "Set1")+
  scale_y_continuous(labels = scales::percent_format(scale = 100), 
                     limits = c(0.25, 0.7), 
                     breaks = seq(0.25, 0.7, by = 0.1)) +
  labs(x = "Wealth Index", y= NULL)+
  theme_minimal()+
  theme(legend.position = "none", axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))



# Contraceptive unmet need by age and location

local_ua <- svyby(
  ~unmet_need ,
  by = ~ age + location_bi,
  design = mysurvey2,
  FUN = svymean,
  vartype = c("se", "ci")
)


# Contraceptive unmet need by education and location

local_ue <- svyby(
  ~unmet_need ,
  by = ~ education + location_bi,
  design = mysurvey2,
  FUN = svymean,
  vartype = c("se", "ci")
)

# Contraceptive unmet need by residence and location
local_ur <- svyby(
  ~unmet_need ,
  by = ~ residence + location_bi,
  design = mysurvey2,
  FUN = svymean,
  vartype = c("se", "ci")
)

# Contraceptive unmet need by wealth index and location
local_uw <- svyby(
  ~unmet_need ,
  by = ~ wealth_index + location_bi,
  design = mysurvey2,
  FUN = svymean,
  vartype = c("se", "ci")
)


# Unmet need by age and location

ual_plot <- local_ua %>%
  ggplot(aes(x = age, y = unmet_need1, color = location_bi, group = location_bi)) +
  geom_point() +
  geom_smooth(se = FALSE) +
  facet_wrap(~location_bi) +
  scale_color_brewer(palette = "Set1")+
  scale_y_continuous(labels = scales::percent_format(scale = 100), 
                     limits = c(0, 0.6), 
                     breaks = seq(0, 0.6, by = 0.1)) +
  labs(x = "Age Group", y= "Unmet Need")+
  theme_minimal()+
  theme(legend.position = "none", axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))


# unmet need by education and location

uel_plot <- local_ue %>%
  mutate(education = factor(education, levels = c("no education", "primary", "secondary", "higher"))) %>%
  ggplot(aes(x = education, y = unmet_need1, color = location_bi, group = location_bi)) +
  geom_point() +
  geom_smooth(se = FALSE, method = lm) +
  facet_wrap(~location_bi) +
  scale_color_brewer(palette = "Set1")+
  scale_y_continuous(labels = scales::percent_format(scale = 100), 
                     limits = c(0, 0.6), 
                     breaks = seq(0, 0.6, by = 0.1)) +
  labs(x = "Education", y= NULL)+
  theme_minimal()+
  theme(legend.position = "none", axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
  

# unmet need by residence and location

url_plot <- local_ur %>%
  ggplot(aes(x = residence, y = unmet_need1, color = location_bi, group = location_bi)) +
  geom_point() +
  geom_smooth(se = FALSE, method = lm) +
  facet_wrap(~location_bi) +
  scale_color_brewer(palette = "Set1")+
  scale_y_continuous(labels = scales::percent_format(scale = 100), 
                     limits = c(0, 0.6), 
                     breaks = seq(0, 0.6, by = 0.1)) +
  labs(x = "Residence", y= "Unmet Need")+
  theme_minimal()+
  theme(legend.position = "none", axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
  

# practice by wealth index and location

uwl_plot <- local_uw %>%
  mutate(wealth_index = factor(wealth_index, levels = c("poorest", "poorer", "middle", "richer", "richest"))) %>%
  ggplot(aes(x = wealth_index, y = unmet_need1, color = location_bi, group = location_bi)) +
  geom_point() +
  geom_smooth(se = FALSE, method = lm) +
  facet_wrap(~location_bi) +
  scale_color_brewer(palette = "Set1")+
  scale_y_continuous(labels = scales::percent_format(scale = 100), 
                     limits = c(0, 0.6), 
                     breaks = seq(0, 0.6, by = 0.1)) +
  labs(x = "Wealth Index", y= NULL)+
  theme_minimal()+
  theme(legend.position = "none", axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

```

### knowledge

```{r}
knowledge_plots <- kal_plot + kel_plot + krl_plot + kwl_plot + plot_annotation(title = "Knowledge level more or less the same between state and region")
knowledge_plots
```

### practice

```{r}
practice_plots <- pal_plot + pel_plot + prl_plot + pwl_plot + plot_annotation(title = "Lower contraceptive use in states across all demographics")
practice_plots
```

### unmet need

```{r}
unmet_plots <- ual_plot + uel_plot + url_plot + uwl_plot + plot_annotation(title = "Higher contraceptive unmet need in states across all demographics")
unmet_plots
```

# Contraceptive map

## Row {.tabset}

```{r}
know_vs_location <- svyby(
  ~knowledge,
  by = ~location,
  design = mysurvey,
  FUN = svymean,
  vartype = c("se", "ci")) %>% 
  rename(name = location)

prac_vs_location <- svyby(
  ~practice,
  by = ~location,
  design = mysurvey,
  FUN = svymean,
  vartype = c("se", "ci")) %>% 
  rename(name = location)

unmet_vs_location <- svyby(
  ~unmet_need,
  by = ~location,
  design = mysurvey2,
  FUN = svymean,
  vartype = c("se", "ci")) %>% 
  rename(name = location)
```


```{r}

data1 <- myanmar %>% 
  left_join(know_vs_location, by = "name") 

data2 <- data1 %>% 
  left_join(prac_vs_location, by = "name")

data3 <- data2 %>% 
  left_join(unmet_vs_location, by = "name") %>% 
  rename(fp_knowledge = knowledge1,
           fp_practice = practice1,
           fp_unmet_need = unmet_need1) %>% 
  pivot_longer(
    cols = starts_with("fp"), 
    names_to = "fp_service", 
    values_to = "fp_proportion")
```



### knowledge map

```{r}
map1 <- data3 %>%
  filter(fp_service == "fp_knowledge") %>%
  ggplot() +
  geom_sf(aes(fill = fp_proportion)) +
  geom_sf_text(aes(label = name), size = 2.5) +
  theme_void() +
  theme(axis.text = element_blank(),
        axis.title = element_blank()) +
  labs(fill = "Knowledge Level", title = "Chin, Rakhine and Shan have lower contraceptive knowledge")

map1

```

### practice map

```{r}
map2 <- data3 %>%
  filter(fp_service == "fp_practice") %>%
  ggplot() +
  geom_sf(aes(fill = fp_proportion)) +
  geom_sf_text(aes(label = name), size = 2.5) +
  theme_void() +
  theme(axis.text = element_blank(),
        axis.title = element_blank()) +
  labs(fill = "Practice Level", title = "Ethnic minority states have significant lower contraceptive use")

map2
```

### unmet need map

```{r}
map3 <- data3 %>%
  filter(fp_service == "fp_unmet_need") %>%
  ggplot() +
  geom_sf(aes(fill = fp_proportion)) +
  geom_sf_text(aes(label = name), size = 2.5) +
  theme_void() +
  theme(axis.text = element_blank(),
        axis.title = element_blank()) +
  labs(fill = "Unmet Need Level", title = "Ethnic minority states have significant higher unmet need")

map3
```



# Contraceptive methods

```{r}
# bonus info

method_use <- dhs_final %>%
  filter(method != "no_use") %>%
  count(method) %>%
  mutate(proportion = round(n / sum(n), 3)) %>%
  mutate(method = reorder(method, proportion)) %>%
  ggplot(aes(x = method, y = proportion)) +
  geom_bar(stat = "identity", fill = "skyblue", width = 0.2) +  
  geom_point(color = "red", size = 2, shape = 8, fill = "maroon") + 
  geom_text(aes(label = scales::percent(proportion)), hjust = -0.2, color = "black", size = 3) +
  labs(title = "Contraceptive methods being used in Myanmar", subtitle = "Injection and pill methods are popular among all available options", caption = "Bonus info",
       x = "Methods",
       y = "Proportion of Usage") +
  scale_y_continuous(labels = scales::percent_format(scale = 100),  limits = c(0, 0.6))+
  theme(plot.title = element_text(size = 11, face = "bold")) +
  coord_flip()

method_use
```


# Data Analysis

## Row {.tabset}

### Regression model


```{r}
#| echo: true
models <- list(
  "practice" = svyglm(practice ~ location_bi + residence + age + education + wealth_index, design = mysurvey, family = binomial(link = "logit")),
  "unmet_need" = svyglm(unmet_need ~ location_bi + residence + age + education + wealth_index, design = mysurvey2, family = binomial(link = "logit"))
)


model_summary <- modelsummary(models, exponentiate = TRUE, coef_rename = c("location_biregion" = "region", "residenceurban" = "urban", "educationhigher" = "edu_higher", "educationprimary" = "edu_primary", "educationsecondary" = "edu_secondary", "wealth_indexmiddle" = "wealth_middle", "wealth_indexpoorer" = "wealth_poorer", "wealth_indexricher" = "wealth_richer", "wealth_indexrichest" = "wealth_richest"), statistic = NULL, output = "flextable")

# note: since level of contraceptive knowledge has no significant difference between state and region, we skipped fitting regression model for knowledge differences.
```

### Outputs

```{r}
model_summary

```








