---
title: "Understanding Health Inequities in Myanmar through DHS data"
author: Wai Linn
format: 
  pdf:
    toc: true
    number-sections: true
    colorlinks: true
    
---

```{r}
# loading required packages

library(tidyverse)
library(shiny)
library(bslib)
library(rnaturalearth)
library(rnaturalearthdata)
library(sf)
library(modelsummary)
```


```{r}
# Creating dataframe for mapping

world <- ne_countries(returnclass = "sf")
myanmar <- ne_states(country = "Myanmar", returnclass = "sf")
```

## Myanmar located in Southeast Asia

Home to longest civil war in the world from 1962 to present day (Why...?)

```{r}
world_mm_map <- world %>%
  mutate(myanmar = case_when(
    name_long == "Myanmar" ~ 1,
    TRUE ~ 0
  )) %>% 
  ggplot(aes(fill = factor(myanmar))) +
  geom_sf() +
  scale_fill_manual(values = c("0" = "gray", "1" = "red")) + 
  theme_minimal() +
  theme(legend.position = "none")

world_mm_map
```


```{r}
# Administratively, 7 states and 7 regions

mm_map1 <- myanmar %>% 
  ggplot()+
  geom_sf(aes(fill = name, color = name)) +
  geom_sf_text(aes(label = name), size = 2.5) +
  theme_void() +
  theme(legend.position = "none")

```


```{r}
# Dividing into two groups

region_colors <- c(
  "Ayeyarwady" = "green",
  "Bago" = "green",
  "Chin" = "red",
  "Kachin" = "red",
  "Kayah" = "red",
  "Kayin" = "red",
  "Magway" = "green",
  "Mandalay" = "green",
  "Mon" = "red",
  "Rakhine" = "red",
  "Sagaing" = "green",
  "Shan" = "red",
  "Tanintharyi" = "green",
  "Yangon" = "green"
)

mm_map2 <- myanmar %>% 
  mutate(ethnicity = ifelse(name %in% c("Kachin", "Kayah", "Kayin", "Kachin", "Chin", "Mon", "Rakhine", "Shan"), "State", "Region")) %>% 
  ggplot() +
  geom_sf(data = myanmar, aes(fill = name)) + 
  scale_fill_manual(values = region_colors) + 
  geom_sf_text(aes(label = ethnicity), size = 2) +
  theme_void() +
  theme(legend.position = "none")
```

## Demographics

::: aside
- 52 million population with ~ 135 ethnic groups. Has 7 states and 7 regions.
- "Bamar" in regions and ">100 ethnic groups" in states
:::



```{r}
mm_map1
```

## Ethnicity


::: aside
- 52 million population with ~ 135 ethnic groups. Has 7 states and 7 regions.
- "Bamar" in regions and ">100 ethnic groups" in states
:::

```{r}
mm_map2
```


## Research Question 

::: {.incremental}
- How do demographic characteristics influence contraceptive knowledge, practices and unmet need among currently married women aged 15-49 in Myanmar?

- Are there any contraceptive disparities between States and Regions?

:::


## Dataset


DHS Myanmar dataset 2016 

- 7870 observations and 26 variables
- All participants are currently married women aged 15-49


Key variables: 

- Demographic characteristics: age (5-yr group), location (region/state), residence (urban/rural), education, wealth index

- Outcome: contraceptive knowledge, practice, unmet need


```{r}
# Required packages for survey weight calculation

library(haven)
library(survey)
library(patchwork)
```

```{r}

# DHS Myanmar dataset 2016

dhs_mm <- read_csv(here::here("data", "dhs_mm.csv"))
```



```{r}
# Variable selection based on research question

dhs_select <- dhs_mm %>% 
  select(caseid, v005, v013, v021, v023, v024, v025, v106, v190, v301, v312, v313, v502, v626a)
```


```{r}
# Creating new and modifying existing variables  

dhs_final <- dhs_select %>% 
  mutate(wt = v005/1000000,
         psu = v021,
         strat = v023) %>% # sampling weight
  filter(v502 == 1) %>% # current married women
  mutate(
    age = case_when(
      v013 == 1 ~ "15-19",
      v013 == 2 ~ "20-24",
      v013 == 3 ~ "25-29",
      v013 == 4 ~ "30-34",
      v013 == 5 ~ "35-39",
      v013 == 6 ~ "40-44",
      v013 == 7 ~ "45-49"
    ),
    location = case_when(
      v024 == 1 ~ "Kachin",
      v024 == 2 ~ "Kayah",
      v024 == 3 ~ "Kayin",
      v024 == 4 ~ "Chin",
      v024 == 5 ~ "Sagaing",
      v024 == 6 ~ "Tanintharyi",
      v024 == 7 ~ "Bago",
      v024 == 8 ~ "Magway",
      v024 == 9 ~ "Mandalay",
      v024 == 10 ~ "Mon",
      v024 == 11 ~ "Rakhine",
      v024 == 12 ~ "Yangon",
      v024 == 13 ~ "Shan",
      v024 == 14 ~ "Ayeyarwady",
      v024 == 15 ~ "Naypyitaw"
    ),
    residence = case_when(
      v025 == 1 ~ "urban",
      v025 == 2 ~ "rural"
    ),
    education = case_when(
      v106 == 0 ~ "no education",
      v106 == 1 ~ "primary",
      v106 == 2 ~ "secondary",
      v106 == 3 ~ "higher"
    ),
    wealth_index = case_when(
      v190 == 1 ~ "poorest",
      v190 == 2 ~ "poorer",
      v190 == 3 ~ "middle",
      v190 == 4 ~ "richer",
      v190 == 5 ~ "richest"
    ),
    method = case_when(
      v312 == 0 ~ "no_use",
      v312 == 1 ~ "pill",
      v312 == 2 ~ "IUD",
      v312 == 3 ~ "injection",
      v312 == 5 ~ "male_condom",
      v312 == 6 ~ "female_sterilization",
      v312 == 7 ~ "male_sterilization",
      v312 == 8 ~ "periodic_abstinence",
      v312 == 9 ~ "withdrawal",
      v312 == 10 ~ "other_traditional",
      v312 == 11 ~ "implant",
      v312 == 13 ~ "lac_amenorrhoea",
      v312 == 17 ~ "other_modern")
  ) %>% 
  mutate(
    knowledge = ifelse(v301 %in% c(3,2), 1, 0),
    practice = ifelse(v313 %in% c(3,2,1), 1,0),
    location_bi = ifelse(v024 %in% c(1, 2, 3, 4, 10, 11 & 13), 0, 1)
  ) %>% 
  mutate(
    location_bi = case_when(
      location_bi == 0 ~ "state",
      location_bi == 1 ~ "region"
    )
  ) %>% 
  mutate(knowledge = factor(knowledge),
         practice = factor(practice))
```


## Key Messages

::: {.incremental}

1. Is it true that there are health inequities between states and regions? 

- The answer is __YES__.

2. Why and How can we address this issue? 

- I suppose this is what the scholars have to find out.

3. __Global health__ is an area for study, research, and practice that places a priority on improving health and achieving _equity in health_ for all people worldwide.

:::




